Summary Tables

### 2021-05-19 summary_tables.Rmd
regen summary tables

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 74.8|23.0|1.0 |
| cycle | 2.3|9.8|1.1 |
| car | 1.0|4.4|6.4 |
| motorcycle | 5.1|33.9|62.9 |
| bus | 15.1|24.3|24.9 |

>>>>

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 95.8|23.8|1.7 |
| cycle | 0.6|0.5|0.2 |
| car | 0.8|16.3|20.6 |
| motorcycle | 0.0|0.0|3.1 |
| bus | 2.4|47.1|62.9 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 65.5|21.2|1.3 |
| cycle | 2.0|8.7|1.0 |
| car | 1.1|4.0|5.8 |
| motorcycle | 5.8|31.7|54.0 |
| bus | 23.9|30.6|34.6 |
